Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Correct conflict errors

## What do the results mean in practice? (limit - 50 words)
Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield. We also don't have data on at what point is starting a fungicide spray schedule is too late. Growers can't scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent. Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in the crop to protect yields.

## What is the key benefit for your readers? (limit - 25 words).
This study is the most robust analysis of management of powdery mildew in mungbean using fungicides. It provide a more certain time frame for growers to plan for when to commence a fungicide spray schedule.
Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.

## What remains unresolved? (no word limit).
Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.
Only a few studies incorporated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.

>>>>

## What do the results mean in practice? (limit - 50 words)  
Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield. We also don’t have data on at what point starting a fungicide spray schedule is too late. Growers can’t scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent. Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in their crop to protect yields.

## what is the key benefit for your readers? (limit - 25 words).  
This study is the most robust analysis of management of powdery mildew in mungbean using fungicides. It provides a more certain time frame for growers to plan when to commence a fungicide spray schedule.

Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.

## What remains unresolved? (no word limit).  
Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.
Only a few studies incorporated in the meta-analysis contained comparisons between the “Late plus” factor and the treatments: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
